---
title: "Getting started with abpwaveforms"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with abpwaveforms}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.width = 7,
  fig.height= 4
)
```

## Overview

abpwaveforms provides Rcpp-accelerated tools to extract fiducials and hemodynamic features from ABP/ECG/PPG signals (inspired by MATLAB BPannotate).

#Main functions

C++ helpers: BP_resample(), doubleDerive(), getFootIndex(), FixIndex(), getPeakIndex(), getDicroticNotchAndPeak()

High-level API: extractFeaturesEnhanced(), process_condition()

```{r setup}
library(abpwaveforms)
```
# Quick start with example data (if shipped)

```{r}
untreated_path <- system.file("extdata", "untreated_signals.csv", package = "abpwaveforms")

if (nzchar(untreated_path)) {
  untreated <- process_condition(untreated_path)
  summary(untreated)
} else {
  message("Example CSVs not found in inst/extdata/. Skipping file demo.")
}


```


## Synthetic demo (runs without files)

```{r}
set.seed(1)
n  <- 5000
fs <- 200
t  <- seq(0, 25, length.out = n)

abp <- 90 + 25*pmax(0, sin(2*pi*1.2*t)) + stats::rnorm(n, 0, 0.5)
ecg <- sin(2*pi*1.2*t) + stats::rnorm(n, 0, 0.1)
ppg <- pmax(0, sin(2*pi*1.2*t)) + 0.1*stats::rnorm(n)

feat <- extractFeaturesEnhanced(abp, ppg, ecg, fs = fs)
head(feat)

```


## Minimal plots

```{r}
op <- par(mfrow = c(1,2))
plot(feat$HR,             type = "l", xlab = "Beat", ylab = "HR (bpm)",          main = "Heart rate")
plot(feat$pulse_pressure, type = "l", xlab = "Beat", ylab = "Pulse Pressure (mmHg)")
par(op)
```



## Tips

C++ helpers return 1-based indices (R-style).

extractFeaturesEnhanced() guards AIx against division-by-zero and interpolates missing PPG samples.

To cap unrealistically high HR, tighten beat spacing when calling FixIndex() (e.g., minIntervalSec = 0.4).

#Reproducibility
```{r}
sessionInfo()
```

